Everything you wanted to know about PanDA but were truly truly afraid to ask

### 2017-03-01 introduction.tex
Notes on introduction
Motivation for HPC and Simulations

>>>>

Why Titan?
\begin{itemize}
    \item A lot of slow (relative the grid) and homogeneous cores together
    \item Grid is saturated
    \item Enable HPC as a calss of computing resource
    \item Enable future DOE experimental and observational capabilities on HPC
    \item Why is so important: more data, run 2 and run 3.
    \item growth of grid is flat (economic model) and saturated. We need more CPU because we have more data.
    \item ATLAS spend most of the time on simulations this is why we want to offload simulations - that happen happen to be performed via AthenaMP.
\end{itemize}
